DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-06 paper/comparison.tex
figure 13
figure 14 revision

In this section, we compare three computing platforms---the Raspberry
Pi 3, the Intel UP~\footnote{http://www.up-board.org/up/} and NVIDIA
Jetson
TX2~\footnote{http://www.nvidia.com/object/embedded-systems-dev-kits-modules.html}---from
the point of view of supporting vision-based end-to-end deep learning
based autonomous vehicles. 
Table~\ref{tbl:platforms} shows architectural features of the three
platforms~\footnote{Note that the GPUs of the Raspberry Pi 3 and Intel
  Up are not used in evaluation due to the lack of software (TensorFlow)
support. Also, the two Denvor cores in Tegra TX2 are not used in
evaluation due to TensorFlow issues.}.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/compare_core}
  \caption{Average control loop execution time.} 
  \label{fig:sys_core}
\end{figure}

Figure~\ref{fig:sys_core} shows the average control loop completion
timing of the four system configurations we tested as a function of
the number of CPU cores used.
First, both the Intel UP and Tegra TX2 exhibit superior performance
compared with the Raspberry Pi 3. 
When all four CPU cores are used, the Intel UP is 2.53X faster than
the Pi 3, while TX (CPU) and TX (GPU) are 3.6X and 7.6X times faster,
respectively, than the Pi 3. 
As a result, they are all able to satisfy the 50 ms 
WCET by a clear margin
%%  (in the worst case, the UP Board would 
%% still meet it by $\sim$20 ms) --> where's the data showing this?
, and, in case of TX2, 50 Hz or even 100 Hz real-time control is
feasible with the help of its GPU.

The UP Board and TX2 also performed better in the multimodel tests, 
as is shown in Figure~\ref{fig:sys_model}. Once again, they were able 
to complete control loops in a fraction of the time when compared to 
the Pi. Furthermore, both of the platforms satisfied the 50 ms WCET 
in all experiments, while the Raspberry Pi 3 was unable to do so. As 
such, the UP Board and TX2 display greater potential for the 
simultaneous execution of multiple models during self-driving 
operation, while the Raspberry Pi 3 would struggle to do so.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/compare_model}
  \caption{Inferencing time across platforms based on number of 
models run concurrently.}
  \label{fig:sys_model}
\end{figure}

Finally, we examined if the performance of the Intel UP Board and 
Tegra TX2 would be affected by the addition of the synthetic 
benchmarks. As summarized in Figure~\ref{fig;sys_bench}, the both 
experienced a change in their inferencing times, but the increases 
were not as drastic as is seen by the Raspberry Pi 3. in the worst 
case, both the UP Board and TX2 (CPU only and GPU) produced times 
that were over two times as large, whereas the Raspberry Pi 3 output 
times that were around 10 times greater. The Intel UP Board was 
successful in completing inferencing operations in under 50 ms when 
benchmarks were run on a maximum of 2 cores, and the TX2 was 
successful in all experiments irrespective of the computing resources 
utilized. Comparetively, both performed better than the Raspberry Pi 
3 which failed to meet its deadlines when any benchmark was 
introduced. As such, it can be concluded that the Intel UP Board 
would be more capable of running computationally heavy processes 
during autonomous driving, and that the Pi wouldn't be able to do the 
same.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/compare_benchmark}
  \caption{Inferencing time across platforms based on number of cores 
used.}
  \label{fig:sys_bench}
\end{figure}

>>>>

In this section, we compare three computing platforms---the Raspberry
Pi 3, the Intel UP~\footnote{http://www.up-board.org/up/} and NVIDIA
Jetson
TX2~\footnote{http://www.nvidia.com/object/embedded-systems-dev-kits-modules.html}---from
the point of view of supporting vision-based end-to-end deep learning
based autonomous vehicles. 
Table~\ref{tbl:platforms} shows architectural features of the three
platforms~\footnote{The GPUs of the Raspberry Pi 3 and Intel
  Up are not used in evaluation due to the lack of software (TensorFlow)
support. Also, the two Denver cores in Tegra TX2 are not used in
evaluation due to TensorFlow issues.}.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/compare_core}
  \caption{Average control loop execution time.} 
  \label{fig:sys_core}
\end{figure}

Figure~\ref{fig:sys_core} shows the average control loop completion
timing of the four system configurations we tested as a function of
the number of CPU cores used.
First, both the Intel UP and Tegra TX2 exhibit superior performance
compared with the Raspberry Pi 3. 
When all four CPU cores are used, the Intel UP is 2.53X faster than
the Pi 3, while TX (CPU) and TX (GPU) are 3.6X and 7.6X times faster,
respectively, than the Pi 3. 
As a result, they are all able to satisfy the 50 ms 
WCET by a clear margin
%%  (in the worst case, the UP Board would 
%% still meet it by $\sim$20 ms) --> where's the data showing this?
, and, in case of TX2, 50 Hz or even 100 Hz real-time control is
feasible with the help of its GPU. Another observation is that TX2
(GPU) does not change much as most of the neural network computation
is done at the GPU.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/compare_model}
  \caption{Average control loop execution time when multiple DNN
    models are co-scheduled. }
  \label{fig:sys_model}
\end{figure}

The UP Board and TX2 also perform much better when multiple DNN models
are co-scheduled. Figure~\ref{fig:sys_model} shows the results of the
multi-model co-scheduling experiment. Once again, they can comfortably
20 Hz real-time performance for all of the co-scheduled DNN control
loops, and in case of TX 2 (GPU), 100 Hz real-time control is still
feasible. Given that the GPU must be shared among the co-scheduled DNN
models, the result suggests that TX2's GPU has sufficient capacity to
accomodate multiple instances of the DNN model we tested.

%% to complete control loops in a fraction of the time when compared to 
%% the Pi. Furthermore, both of the platforms satisfied the 50 ms WCET 
%% in all experiments, while the Raspberry Pi 3 was unable to do so. As 
%% such, the UP Board and TX2 display greater potential for the 
%% simultaneous execution of multiple models during self-driving 
%% operation, while the Raspberry Pi 3 would struggle to do so.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/compare_benchmark}
  \caption{Inferencing time across platforms based on number of cores 
used.}
  \label{fig:sys_bench}
\end{figure}

Finally, we compare the effect of co-scheduling memory intensive
synthetic benchmarks on the DNN control loop timing.
Figure~\ref{fig:sys_bench} shows the results. 
experienced a change in their inferencing times, but the increases 
were not as drastic as is seen by the Raspberry Pi 3. in the worst 
case, both the UP Board and TX2 (CPU only and GPU) produced times 
that were over two times as large, whereas the Raspberry Pi 3 output 
times that were around 10 times greater. The Intel UP Board was 
successful in completing inferencing operations in under 50 ms when 
benchmarks were run on a maximum of 2 cores, and the TX2 was 
successful in all experiments irrespective of the computing resources 
utilized. Comparetively, both performed better than the Raspberry Pi 
3 which failed to meet its deadlines when any benchmark was 
introduced. As such, it can be concluded that the Intel UP Board 
would be more capable of running computationally heavy processes 
during autonomous driving, and that the Pi wouldn't be able to do the 
same.

### 2017-10-06 paper/evaluation.tex
figure 14 revision

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/perf_vs_modelcnt}
  \caption{Timing impact of co-scheduling multiple DNNs. 1x1: one DNN
    model using one CPU core; 4x1: four DNN models each using one CPU;
    1x2: one DNN model using two CPU cores; 2x2: two DNN models each
    using two CPU cores.} 
  \label{fig:perf-vs-modelcnt}
\end{figure}

@@

\begin{table*}[h]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    Item    & Raspberry Pi 3 (B)   & Intel UP                  & NVIDIA Jetson TX2\\
    \hline
            & BCM2837              & X5-Z8350 (Cherry Trail)   & Tegra TX2 \\
    CPU     & 4x Cortex-A53@1.2GHz/512KB L2  &
              4x Atom@1.92GHz/2MB L2 &
              4x Cortex-A57@2GHz/2MB L2 \\
            &              &              & 2x Denver@2.0GHz/2MB L2 (not used)  \\
    \hline
    GPU     &  VideoCore IV (not used)    &
               Intel HD 400 Graphics (not used) &
               Pascal 256 CUDA cores   \\
    \hline
    Memory  & 1GB LPDDR2   &  2GB DDR3L     & 8GB LPDDR4              \\
    \hline
  \end{tabular}
  \caption{Compared embedded computing platforms}
  \label{tbl:platforms}
\end{table*}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/perf_vs_modelcnt}
  \caption{Timing impact of co-scheduling multiple DNNs. 1Nx1C: one DNN
    model using one CPU core; 4Nx1C: four DNN models each using one CPU;
    1Nx2C: one DNN model using two CPU cores; 2Nx2C: two DNN models each
    using two CPU cores.} 
  \label{fig:perf-vs-modelcnt}
\end{figure}

@@

\begin{table*}[h]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    Item    & Raspberry Pi 3 (B)   & Intel UP                  & NVIDIA Jetson TX2\\
    \hline
            & BCM2837              & X5-Z8350 (Cherry Trail)   & Tegra X2 \\
    CPU     & 4x Cortex-A53@1.2GHz/512KB L2  &
              4x Atom@1.92GHz/2MB L2 &
              4x Cortex-A57@2GHz/2MB L2 \\
            &              &              & 2x Denver@2.0GHz/2MB L2 (not used)  \\
    \hline
    GPU     &  VideoCore IV (not used)    &
               Intel HD 400 Graphics (not used) &
               Pascal 256 CUDA cores   \\
    \hline
    Memory  & 1GB LPDDR2   &  2GB DDR3L     & 8GB LPDDR4              \\
    \hline
  \end{tabular}
  \caption{Compared embedded computing platforms}
  \label{tbl:platforms}
\end{table*}
